Signed-distance-field local geometry feedforward provides a low-intrusion way to improve complementarity-based rigid-body contact without rewriting the underlying solution chain. This paper presents a complementarity-based rigid-contact model built around that idea. Within a Moreau--Jean framework, local geometric information from a signed distance field is used to construct regime-dependent contact representations. Smooth continuously evolving contact is treated with a persistent-manifold SlidingPatch representation augmented by Hessian-based curvature feedforward, whereas contact onset, compact contact zones, and switching-sensitive cases are handled with a more conservative CompactDiscrete representation. The geometric correction is introduced only through a feedforward modification of the effective normal gap, so the underlying linear complementarity problem (LCP) solution chain is preserved.

Results from head-on impact, an eccentric disk--roller analytical benchmark, the Onset Stress Benchmark, an industrial cam, and a Twin Gear case show that regime-matched local-geometry-aware modeling improves gap prediction and reduces trajectory and velocity errors while keeping the additional modeling overhead controlled. The gain is most evident in sustained-sliding and contact-onset scenarios. Near singular boundaries or under nonsmooth meshing, more conservative discrete representations provide better robustness. The benchmarks support two conclusions: the full local-geometry-aware modeling stack is effective within a complementarity-based rigid-contact framework, and curvature feedforward yields additional gains when the underlying local manifold remains smooth. Overall, the proposed method is a regime-matched modeling strategy that improves contact-response accuracy without sacrificing computational efficiency under clearly stated applicability conditions.
